### 2014-07-18 Docs/managing_jobs/managingjobs.tex
merge the compiler stuff into here

All plotfile directories have a {\tt job\_info} file which lists as
host of parameters about the simulation, including:
\begin{itemize}
\item A descriptive name for the simulation (the {\tt job\_name} runtime
  parameter
\item The number of MPI tasks and OpenMP threads
\item The total amount of CPU-hours used up to this point
\item The data and time of the plotfile creation and the directory it was written to.
\item The build date, machine, and directory
\item The MAESTRO, BoxLib and other relevant git hashes for the source
\item The directories used in the build
\item The compilers used and compilation flags
\item The number of levels and boxes for the grid
\item The properties of the species carried
\item The tolerances for the MG solves
\item Any warnings from the initialization procedure (note: these are not currently stored on restart).
\item The value of all runtime parameters (even those that were not explicitly set in the inputs file), along with an indicator showing if the default value
was overridden.
\end{itemize}
This file makes it easy to understand how to recreate the run that
produced the plotfile.

@@

@@

>>>>

All plotfile directories have a {\tt job\_info} file which lists as
host of parameters about the simulation, including:
\begin{itemize}
\item A descriptive name for the simulation (the {\tt job\_name} runtime
  parameter
\item The number of MPI tasks and OpenMP threads
\item The total amount of CPU-hours used up to this point
\item The data and time of the plotfile creation and the directory it was written to.
\item The build date, machine, and directory
\item The \maestro, \boxlib, and other relevant git hashes for the source
\item The directories used in the build
\item The compilers used and compilation flags
\item The number of levels and boxes for the grid
\item The properties of the species carried
\item The tolerances for the MG solves
\item Any warnings from the initialization procedure (note: these are not currently stored on restart).
\item The value of all runtime parameters (even those that were not explicitly set in the inputs file), along with an indicator showing if the default value
was overridden.
\end{itemize}
This file makes it easy to understand how to recreate the run that
produced the plotfile.

\section{Linux boxes}

\subsection{gfortran}

gfortran is probably the best compiler for \maestro.  Here are some
version-specific notes:

\begin{itemize}
\item {\em gfortran 4.5.x}: gfortran 4.5 has no known issues.

\item {\em gfortran 4.6.x}: gfortran 4.6.1--4.6.3 on Fedora 
(15 and 16) have a bug that shows up in multi-processor, multilevel
runs ({\tt toy\_convect} on 4 processors, with {\tt
inputs\_2d\_ml.test} for instance).  The symptom is a crash during
initialization with the message that ``message sizes do not match
across processes in the collective'' in a {\tt parallel\_bcast} call.
This is in {\tt cluster\_f.f90}, and the issue seems to be a
multiplication error in computing the size to allocate {\tt bxs}.  The
bug is not present when you compile in debug mode, so it seems to be
related to optimization.

\item {\em gfortran 4.7.x}: gfortran 4.7.1 (prerelease) seems to have 
fixed the above issue, but now wdconvect with 2-level, effective
768$^3$ dies due to an unknown seg fault at the beginning of the run.

\item {\em gfortran 4.8.x}: There are no known issues with gfortran 4.8.x

@@

\subsection{Titan Compilers}

The preferred compilers on Titan are the Cray compilers.  
Cray 8.2.5 works well on titan/OLCF with MPI/OpenMP.

@@

\subsection{edison compilers}

The default compilers on edison are the Intel compilers, but
it seems that the Cray compilers are the best.

\begin{itemize}
\item Cray 8.2.6 works well on edison/NERSC with MPI/OpenMP.

\item Cray 8.3.0 generates an internal compiler error on edison/NERSC.
      To get back to the older Cray compilers, you need to do:
\begin{verbatim}                                                                                  
module swap cce/8.3.0 cce/8.2.6                                                                   
module swap cray-libsci cray-libsci/12.2.0                                                        
module swap cray-mpich cray-mpich/6.3.1                                                           
\end{verbatim}
\end{itemize}
